---
title: "using readAntares"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using readAntares}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(antaresRead)
library(DependenciesGraphs)
```

# Dependecies analyse

```{r}
dep <- funDependencies("package:antaresRead","readAntares")
plot(dep, height = "500px", width = "100%")
```


  

## Part 1 - Check function parameter and management  

See in function :

 - minor checks (renewables)  
 - `.giveSize()` private function to check size  
   - If size is too big (10GB or 70% RAM size)  
 - `.giveInfoRequest` : transform inputs arguments to be passable to reading function  
 - `aggregateResult()` is called if parameter `mcWeights` is not null  
 
 
## Part 2 - Add data from study output 

Several calls to private functions to output data :  

  - `.importOutputForAreas()`  
  - `.importOutputForLinks()`  
  - ...  
  - 
  
Or private functions to input data :  

 - `.addOutputToRes("misc", areas, .importMisc)` (`.addOutputToRes()` is launcher)

